Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-01 paper/paper.tex
minor changes

\begin{figure}[t!]

@@

  \scalebox{0.9}{  

@@

    \scalebox{0.9}{  

@@

  \\

@@

\end{figure}

@@

\renewcommand{\arraystretch}{0.9}

@@

  \begin{tabular}{lcccp{10cm}}

@@

\renewcommand{\arraystretch}{0.7}
\setlength{\tabcolsep}{2pt}
\begin{table}[t!]
  \footnotesize
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Vars.}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

\begin{center}
\begin{tcolorbox}[enhanced,width=3.3in,center upper,drop shadow southwest,sharp corners]
\tname\ successfully synthesizes the golden rules in all cases and
that rule is ranked among the top five rules in
\percTopFiveRanking\ of the cases.
\end{tcolorbox}
\end{center}

@@

\begin{table}[h!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}  
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    2100384 & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    2100399 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    2100401 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100402 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100408 & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    2100485 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    2100486 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 4 & 4 & 2\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 87 & 87 & 15\cellcolor{lightgray}$\downarrow$ & 84 & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 17 & 17 & 144$\uparrow$ & 27$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 1 & 1 & 15$\uparrow$ \\
    /system32/ in URI & 2  & 2 & 6$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$\\
    Basebuilder LFI & 48  & 48 & 846$\uparrow$ & 65$\uparrow$ & 664$\uparrow$\\
    Tomcat Snoop Access & 37  & 37 & 1797$\uparrow$ & 6\cellcolor{lightgray}$\downarrow$ & 3580$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{center}
\begin{tcolorbox}[enhanced,width=3.4in,center upper,drop shadow southwest,sharp corners]
Every function showed impact on the performance of \tname. The function that builds on popularity of content
modifiers showed highest impact.
%The function that builds on  was the one that affected positively the higher number of
%cases we analyzed.
\end{tcolorbox}
\end{center}

@@

This section evaluates sensitivity of \tname{} to the amount of
examples provided on input. Recall that \tname\ uses one example
attack to generate the seed rule (at the Reverse Engineering step) and
the remaining attacks to evaluate soundness of the rule (at the Rules
Creations step). It is expected that the number and variety of attacks
play a role in the performance of the technique.

\begin{figure}[h]
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=10 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}       \caption{scripttag}    
  \end{subfigure}%
%\vspace{1ex}  
\caption{Impact of number of positive examples.}
\label{fig:impact-number-attacks}
%\vspace{1ex}
\end{figure}

We answer this question in two parts. Firts, we analyzed the impact of
the amount of positive examples in results. For that, we selected two
cases with the highest number of examples (see column ``\#~Vars'' on
Table~\ref{table:results})---idqaccess and scripttag and measured the
position of the golden rule at the rank for an increasing number of
examples provided to \tname. For each number of variants, we sampled
five sets of that size to provide as input to the
technique. Figure~\ref{fig:impact-number-attacks} shows the results
for each attack we selected. The y-axis of each plot denotes the rank
of the golden rule and x-axis denotes the number of attack examples
used to synthesize rules. Each point in the x-axis is associated with
the boxplot of the distribution of results for the corresponding
number of variants. Results indicate that 1) the number of examples is
important, 2) the choice of examples is important, and 3) a small
number of examples suffices to reach the best results.

@@

\begin{center}
\begin{tcolorbox}[enhanced,width=3.5in,center upper,drop shadow southwest,sharp corners]
\tname\ is sensitive to the number and choice of examples. However, a
small number of positive examples suffices to achieve good results.
\end{tcolorbox}
\end{center}

>>>>

\begin{figure*}[t!]

@@

  \scalebox{0.8}{  

@@

    \scalebox{0.85}{  

@@

%  \\

@@

\end{figure*}

@@

%renewcommand{\arraystretch}{0.9}

@@

  \setlength{\tabcolsep}{4.5pt}
  \renewcommand{\arraystretch}{0.35}
  \begin{tabular}{lcccp{11cm}}

@@

%\renewcommand{\arraystretch}{0.7}
%\setlength{\tabcolsep}{2pt}
\begin{table}[t!]
  \footnotesize
  \setlength{\tabcolsep}{2pt}
  \renewcommand{\arraystretch}{0.5}
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Vars.}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

%% \begin{center}
%% \begin{tcolorbox}[enhanced,width=3.3in,center upper,drop shadow southwest,sharp corners]
%% \tname\ successfully synthesizes the golden rules in all cases and
%% that rule is ranked among the top five rules in
%% \percTopFiveRanking\ of the cases.
%% \end{tcolorbox}
%% \end{center}

\emph{ \textbf{Summary of results:}~\tname\ successfully synthesizes
  the golden rules in all cases and that rule is ranked among the top
  five rules in \percTopFiveRanking\ of the cases.  }

@@

\begin{table}[h!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}
  %\setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{-0.01}
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    2100384 & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    2100399 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    2100401 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100402 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100408 & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    2100485 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    2100486 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 4 & 4 & 2\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 87 & 87 & 15\cellcolor{lightgray}$\downarrow$ & 84 & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 17 & 17 & 144$\uparrow$ & 27$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 1 & 1 & 15$\uparrow$ \\
    /system32/ in URI & 2  & 2 & 6$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$\\
    Basebuilder LFI & 48  & 48 & 846$\uparrow$ & 65$\uparrow$ & 664$\uparrow$\\
    Tomcat Snoop Access & 37  & 37 & 1797$\uparrow$ & 6\cellcolor{lightgray}$\downarrow$ & 3580$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

@@

%% \begin{center}
%% \begin{tcolorbox}[enhanced,width=3.4in,center upper,drop shadow southwest,sharp corners]
%% %The function that builds on  was the one that affected positively the higher number of
%% %cases we analyzed.
%% \end{tcolorbox}
%% \end{center}

\emph{\textbf{Summary of results:}~Every function showed impact on the
  performance of \tname. The function that builds on popularity of
  content modifiers showed highest impact.}

@@

This section evaluates sensitivity of \tname{} to the amount of
examples provided on input. Recall that \tname\ uses one example
attack to generate the seed rule (at the Reverse Engineering step) and
the remaining attacks to evaluate soundness of the rule (at the Rules
Creations step). It is expected that the number and variety of attacks
play a role in the performance of the technique.  We answered this
question in two parts. First, we analyzed the impact of the amount of
positive examples in results. For that, we selected two cases with the
highest number of examples---idqaccess and scripttag---and measured
the position of the golden rule at the rank for an increasing number
of examples provided to \tname. For each number of variants, we
sampled five sets of that size to provide as input to the technique.

% (see column ``\#~Vars'' on Table~\ref{table:results})

\begin{figure}[h]
  \vspace{-2ex}
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=10 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}       \caption{scripttag}    
  \end{subfigure}%
  \caption{\label{fig:impact-number-attacks}Impact of number of positive examples.}
  \vspace{-2ex}
\end{figure}

Figure~\ref{fig:impact-number-attacks} shows the results for each
attack we selected. The y-axis of each plot denotes the rank of the
golden rule and x-axis denotes the number of attack examples used to
synthesize rules. Each point in the x-axis is associated with the
boxplot of the distribution for the corresponding number of
variants. Results indicate that the number of examples is important,
the choice of examples is important, and a small number of examples
suffices to reach the best results.

@@

%% \begin{center}
%% \begin{tcolorbox}[enhanced,width=3.5in,center upper,drop shadow southwest,sharp corners]

%% \end{tcolorbox}
%% \end{center}

\emph{ \textbf{Summary of results:}~\tname\ is sensitive to the number
  and choice of examples. However, a small number of positive examples
  suffices to achieve good results.}
